\documentclass[handout]{beamer}
% \documentclass{beamer}

\input{../lecture-setup.tex}

\title{}
\title{Cool Stuff With Lines}
\date{April 17, 2017}


\begin{document}
\small

\section*{Administration}

\frame{
  \frametitle{Office Hours!}
  % \ \vspace*{0.25in}

  {\Large{}Instructor:}\\
  \ \hspace*{0.2in} Peter M.\ Garfield, \url{garfield@math.ucsb.edu}\\[0.25em]

  {\Large{}Office Hours:}\\
  \ \hspace*{0.2in} Mondays 1--2\textsc{pm}\\
  \ \hspace*{0.2in} Tuesdays 10:30--11:30\textsc{am}\\
  \ \hspace*{0.2in} Thursdays 1--2\textsc{pm}\\
  \ \hspace*{0.2in} or by appointment \\[0.25em]

  {\Large{}Office:}\\
  \ \hspace*{0.2in} South Hall 6510\\[0.5em]

  \copyright\ 2017\ Daryl Cooper, Peter M.\ Garfield

  % \vspace*{2in}
}

\section*{Proportionality}

\frame{
  \frametitle{Proportionality Review}

  
  ``$y$ is proportional to $x$'' or $y\propto x$ means
  \begin{itemize}
  \item When we double $x$, we double $y$
    \pause

  \item When we triple $x$, we triple $y$
    \pause

  \item When we halve $x$, we halve $y$
    \pause

  \item $y=Kx$, where $K$ is called the
  \alert{\emph{constant of proportionality}}. 

  \end{itemize}

  \vspace*{1in}



}

\frame{
  \frametitle{Constant of Proportionality}

  \alert{Example:}\ We are told
  \begin{itemize}
  \item Tax is proportional to income, and 
  \item The tax on \$$1,000$\ is \$$280$.
  \end{itemize}
  Express $y = \text{amount of tax paid}$\ in terms of  $x = \text{the
    income}$. Then $y=$
  \begin{center}
    \mbox{
      A$= 1000x$
      \quad 
      B$= 280x$
      \quad 
      C$=\dfrac{1,000}{280}\,x$
    }
    \\[0.5em]
    \mbox{
      D$=2.8x$
      \quad 
      E$= 0.28x$
      \pause
      \quad 
      \answer{E} 
    }
  \end{center}
  \gap

  \alert{Question:}\ What does the constant of proportionality
  $K=0.28$ mean?
  \pause\halfgap

  \alert{Answer:}\ It is the tax on one dollar.


}


\frame{
  \frametitle{Example}

  For this question, we assume:
  \begin{itemize}
  \item   The weight of an elephant is proportional to its
    \alert{\emph{height cubed}}, and

  \item   An elephant 1 meter high weighs $1/3$ tons. 
  \end{itemize}

  How many tons does an elephant $h$ meters tall weigh?
  \begin{center}
    A$= h/3$
    \quad 
    B$= h^3$
    \quad 
    C$ = h^3/3$
    \quad 
    D$ = (h/3)^3$
    \quad 
    E$ = (3h)^3$
    \pause
    \quad
    \answer{C}
  \end{center}
  \gap

  \alert{Question:}\ What does the constant of proportionality
  $K=1/3$ mean?
  \pause\halfgap

  \alert{Answer:}\ It is the weight of $1$ cubic meter of elephant.

}

\frame{
  \frametitle{More Complicated Examples}
  
  \begin{empheq}[box=\othermathbox]{equation*}
    \text{$y$ is \alert{inversely proportional} to $x$ means $y\propto 1/x$}
  \end{empheq}
  \pause

  Example:
  \begin{itemize}
  \item I have \$$300$
  \item $N=$ number of apples I can buy
  \item $p=$ price per apple
  \end{itemize}
  Then $N$ is inversely proportional to $p$: $N\propto 1/p$.
  \bigskip
  \pause

  \alert{Question:}\ What is the constant of proportionality?
  \smallskip
  \pause

  \alert{Answer:}\ It is \$$300$, the amount of money I have.
  \gap

}

\frame{
  \frametitle{More Complicated Examples}
  
  \begin{empheq}[box=\othermathbox]{equation*}
    \text{$z$ is \alert{jointly proportional} to $x$ and $y$ means $x\propto
      x\cdot y$ (or $z=Kxy$)}
  \end{empheq}
  \pause

  Example:
  \begin{itemize}
  \item $C =$ cost of a rectangular plot of land,
  \item $\ell=$ length (in meters) of plot, and
  \item $w=$ width (in meters) of plot.
  \end{itemize}
  Then $C$ is jointly proportional to $\ell$ and $w$: $C=K\cdot \ell
  \cdot w$.
  \bigskip
  \pause

  \alert{Question:}\ What does the constant of proportionality mean?
  \pause
  \smallskip

  \alert{Answer:}\ It is the cost of one square meter of land.



}

\frame{
  \frametitle{More Complicated Examples}

  \alert{\large{}Strength of Light}\
  \begin{itemize}
  \item $P\;$\parbox[t]{2.5in}{%
      $=\text{strength of light (\colorbox{yellow}{power}\ per unit area)}$ \\
      \pause%
      $=\text{amount of light on unit area}$
    }
    \pause

  \item $R = $ distance to light source
    \pause
  \end{itemize}
  \gap

  \alert{Inverse Square Law:}\ $P\propto 1/R^2$
  \pause
  \gap

  Same idea for heat, gravity, sound, and many others\ldots
  \pause
  \gap

  \alert{Newton's Law of Gravity:}\ $F \propto \dfrac{m_1m_2}{r^2}$
  \pause
  \halfgap

  Constant of proportionality: 
  \parbox[t]{2in}{%
    $G\approx 6.67\times 10^{-11}\ \text{m}^3/(\text{kg}\,\cdot\,
    \text{s}^{2})$\\[0.25em]
    (the \colorbox{yellow}{Gravitational constant})
  }

}

\section*{Review}

\frame{
  \frametitle{Winter 17 Exam \#1}

  \begin{enumerate}
  \item Solve for $x$ in the equation
    \begin{equation*}
      \frac{3}{x+a} = \frac{a}{x+2}.
    \end{equation*}
    \vspace*{0.5in}
    \pause

  \item Multiply out and simplify.  Check your answer.
    \begin{equation*}
      (a-3b)(4a+2b) + 6ab
    \end{equation*}
    \vspace*{0.5in}
  \end{enumerate}

}

\frame{
  \frametitle{Winter 17 Exam \#1}

  \begin{enumerate}
    \setcounter{enumi}{2}
  \item Substitute $x=3t-4$\ into
    \begin{equation*}
      2x(x+1).
    \end{equation*}
    Simplify the result as much as possible. 
    \vspace*{0.5in}
    \pause

  \item Solve for $x$ and $y$ in the simultaneous equations
    \begin{equation*}
      x+2y=p
      \qquad\qquad
      x+y=4.
    \end{equation*}
    \vspace*{0.5in}
  \end{enumerate}
}


\frame{
  \frametitle{Winter 17 Exam \#1}

  \begin{enumerate}
    \setcounter{enumi}{4}
  \item Marie leaves Santa Barbara at 10am, driving to Bakersfield on
    a route which is $150$\ miles\ long.  Jason leaves Bakersfield at
    11am driving the same route to Santa Barbara.  Marie's speed is
    $40\ \text{miles}/\text{hr}$\ and Jason's speed is
    $60\ \text{miles}/\text{hr}$.
    \vspace*{0.2in}
    \begin{enumerate}
      \item[\colorbox{blue!25}{(a)}] How far apart are they at noon?
        \vspace*{0.2in}
        \pause

      \item[\colorbox{blue!25}{(b)}] How far from Santa Barbara are
        they when they meet? 
        \vspace*{0.2in}
        \pause
        
      \item[\colorbox{blue!25}{(c)}] How many hours has \emph{Jason}\
        been driving when they meet?\\ 
        {\tiny[leave your answers as \emph{fractions}]}
        \vspace*{0.2in}

    \end{enumerate}
  \end{enumerate}
}

\frame{
  \frametitle{Winter 17 Exam \#1}

  \begin{enumerate}
    \setcounter{enumi}{5}
  \item A farmer wants to partition a rectangular field into quarters,
    as shown.  The total area of the field is $500$\ square
    meters. Suppose the length of the field is $L$ meters.

    \begin{minipage}[t]{0.450\linewidth}
      \begin{enumerate}
      \item[\colorbox{blue!25}{(a)}] Express the width of the field in
        terms of $L$. \\[0.5em] 
      \end{enumerate}
    \end{minipage}
    \begin{minipage}[t]{0.50\linewidth}
      \begin{center}
        \begin{tikzpicture}[x=10mm,y=25mm,>=latex,baseline=25mm]
          \draw[thin,black,<->] (-0.3,0) -- (-0.3,1) node[midway,fill=white,rotate=90] {$L$};
          \draw[thin,black,<->] (0,1.1) -- (4,1.1) node[midway,fill=white] {$width$};
          \draw[ultra thick,black] (0,0) rectangle (4,1);
          \draw[ultra thick,black,dotted] (0,0.5) -- (4,0.5);
          \draw[ultra thick,black,dotted] (2,0) -- (2,1);
        \end{tikzpicture}
      \end{center}
    \end{minipage}
    % \bigskip
    \begin{enumerate}
      \item[\colorbox{blue!25}{(b)}] 
      The outer boundary fence (on the perimeter of the field, shown solid)
      costs \$$4$ per meter, and the inside fence (shown dotted) costs
      \$$3$ per meter. Express the total cost of the fence needed in terms
      of $L$.
      % Express the total number of meters of fence needed in terms of $L$.
      % \bigskip
    \end{enumerate}
  \end{enumerate}



}



\end{document}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 
