\documentclass[letterpaper]{article}
%\documentclass[a5paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}


%% Sets page size and margins
\usepackage[letterpaper,top=.75in,bottom=1in,left=1in,right=1in,marginparwidth=1.75cm]{geometry}
%\usepackage[a5paper,top=1cm,bottom=1cm,left=1cm,right=1.5cm,marginparwidth=1.75cm]{geometry}

\usepackage{graphicx}
%\graphicspath{../images}	  %%where to look for images

\input{../tskpreamble}

\pgfplotsset{compat=1.13}

%\newcommand{\T}{\mathcal{T}}
%\newcommand{\B}{\mathcal{B}}

%These commands are now in tskpreamble_nothms.tex, but are left as a comment here for reference. 
%\newcommand{\arbcup}[1]{\bigcup\limits_{\alpha\in\Gamma}#1_\alpha}
%\newcommand{\arbcap}[1]{\bigcap\limits_{\alpha\in\Gamma}#1_\alpha}
%\newcommand{\arbcoll}[1]{\{#1_\alpha\}_{\alpha\in\Gamma}}
%\newcommand{\arbprod}[1]{\prod\limits_{\alpha\in\Gamma}#1_\alpha}
%\newcommand{\finitecoll}[1]{#1_1, \ldots, #1_n}
%\newcommand{\finitefuncts}[2]{#1(#2_1), \ldots, #1(#2_n)}
%\newcommand{\abs}[1]{\left|#1\right|}
%\newcommand{\norm}[1]{\left|\left|#1\right|\right|}

\title{Pre-Calculus \linebreak
Test 3}
\author{Mr. Klar}
\date{}

\begin{document}

\maketitle

\noindent	\textbf{Use the 3 famous points to write a short table of values for the function. Then sketch a graph of the function. Identify any asymptotes and intercepts. (Hint: Choose values of $x$ so that the entire exponent becomes a famous point.)}
\begin{enumerate}
	\item $f(x) = -2^{x+3}$ 
	\item $f(x) = 1+e^{2x}$
\end{enumerate}
\noindent	\textbf{Evaluate the expression without a calculator.}
\begin{enumerate}\setcounter{enumi}{2}
\item $\log_{1.23}{1.23}^{456}$
\item $2\ln e^{3.14}$
\item $5-\log_{10}(1000)$
\end{enumerate}
\noindent	\textbf{Use the 3 famous points to sketch the parent function. Then use transformations to sketch the given function. (You can erase the parent function once you're done with it if you want.)}
\begin{enumerate}\setcounter{enumi}{5}
\item $f(x) = -\ln(x)+2$
\item $f(x) = 1+2\log_{3}(x+3)$
\end{enumerate}
\noindent	\textbf{Rewrite the log with base 10 by using change-of-base formula.}
\begin{enumerate}\setcounter{enumi}{7}
\item $\log_{17} 92$
\end{enumerate}
\noindent	\textbf{Use the properties of logarithms to expand the expression as a sum or difference of logs with no exponents or radicals.}
\begin{enumerate}\setcounter{enumi}{8}
\item $\log_3 2b^4$
\item $\ln\dfrac{x\sqrt{x+1}}{3e^4}$
\end{enumerate}
\noindent	\textbf{Condense the expression to a single logarithm.}
\begin{enumerate}\setcounter{enumi}{10}
\item $3\log_3 x+4\log_3 y^2$
\item $\ln 3x -\ln(x-3) + \ln(x^2-9)$
\end{enumerate}
\noindent	\textbf{Solve for $x$. Use the fact that $\log_5(2)\approx 0.43$. (Hint: Factor large numbers to simplify logs. You can use my "lame calculator" for the decimal arithmetic.)}
\begin{enumerate}\setcounter{enumi}{12}
\item $3^x = 81$
\item $5^{2x}=250$ 
\item $\log_6 x=3$
\item $\log_{10}(x+3)=4$
\end{enumerate}
\noindent	\textbf{Solve the equation algebraically. Write your answer in terms of logs with no exponents or radicals.}
\begin{enumerate}\setcounter{enumi}{16}
\item $\dfrac{1025}{8+e^{4x}}=5$
\item $-xe^{-x}+e^{-x}=0$ \quad (Hint: use the Zero Product Property)
\item[Bonus.] $\log_{10}(x)-\log_{10}(8-5x)=2$
\end{enumerate}

\end{document}
