 \documentclass[12pt,letterpaper]{article}

\usepackage{fancyhdr,fancybox,tensor}

\input{tskpreamble_nothms} %find me at /home/trevor/texmf/tex/latex/tskpreamble_nothms.tex
\input{tsktheoremstyles}

%%
%% Page set-up:
%%
\pagestyle{empty}
\lhead{\textsc{201c - Functional Analysis} \\Quarter of COVID-19} 
\rhead{\textsc{Labutin, Spring 2020} \\ Trevor Klar}
%\chead{\Large\textbf{A New Integration Technique \\ }}
\renewcommand{\headrulewidth}{0pt}
%
\renewcommand{\footrulewidth}{0pt}
%\lfoot{
%Office: \quad \quad \, M 2-3 \, \, SH 6431x \\
%Math Lab: \, W 12-2 \, SH 1607
%}
%\rfoot{trevorklar@math.ucsb.edu}

\setlength{\parindent}{0in}
\setlength{\textwidth}{7in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\parskip}{.5\baselineskip}
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{9in}

\setlist[enumerate,1]{label=\textbf{\arabic*.}}

\let\oldphi\phi
\renewcommand{\phi}{\varphi}
\renewcommand{\epsilon}{\varepsilon}

\begin{document}
\pagestyle{fancy}
\begin{center}
{\Large Homework 6}%=================UPDATE THIS=================%
\end{center}

\renewcommand{\B}{\bar{B}(\ell^\infty)}
\textbf{Chapter 5}

\begin{enumerate}
\setcounter{enumi}{1}
\item Prove the Reimann-Lebesgue lemma mentioned in Section 5.1., i.e., for $f\in L^1(\R^n)$, 
$$\hat{f}(k)\to 0\text{ as }k\to \infty.$$
[\textit{Hint}. 5.3(1) is useful. 
\jpg{width=0.9\textwidth}{plancharel-thm-5-3-1}
\begin{proof}
I didn't have time to do all of these problems, since this week we have a midterm in this class and another class, in addition to the regular work which I can barely keep up with. 
\end{proof}

\setcounter{enumi}{4}
\item Complete the proof of Theorem 5.8, i.e., work out the approximation
argument mentioned at the end of Sect. 5.8:
\jpg{width=.9\textwidth}{theorem-5-8}

\begin{proof}
Let $h,u\in C^\infty_0(\R^n)$. In particular, $h,u\in L^1(\R^n)$, so $\widehat{h*u}=\hat h \hat u$ by (1). Now consider the operators 
\begin{align*}
T:L^p(\R^n)\times L^q(\R^n) &\to L^\infty(\R^n) \text{ given by}\\
 (f,g)&\mapsto f*g\\
 \\
S:L^p(\R^n)\times L^q(\R^n) &\to L^{r'}(\R^n) \text{ given by}\\
 (f,g)&\mapsto \hat f \hat g\\
 \\
\hat \bigcdot : L^{r'}&\to C_0 \text{, the Fourier Transform,}
\end{align*}
all of which are clearly continuous operators. Observe that $\hat \bigcdot \circ T = S$ on $C^\infty_0\times C^\infty_0$, and thus we have two continuous maps which agree on a dense subset of their domains, so they agree everywhere. 
\end{proof}

\item %For $f\in C^\infty_c(\R^n)$ show that its Fourier transform $\hat{f}$ is also in $C^\infty$. Show also that 
%$$g_a(k):=$$
\mbox{}\vspace*{-28pt}
\jpg{width=0.99\linewidth}{hw6-ch5-p6}
\begin{proof}
I didn't have time to do all of these problems, since this week we have a midterm in this class and another class, in addition to the regular work which I can barely keep up with. 
\end{proof}

\setcounter{enumi}{8}
\item Verify that 5.6(1) cannot hold when $\rho > 2$ by considering Gaussian 
functions, as in 5.2(1), with $\lambda=a+ib$ and with $a>0$. 

\jpg{width=0.99\linewidth}{5-6(1)-title}
\jpg{width=0.99\linewidth}{5-6(1)}
\jpg{width=0.99\linewidth}{theorem-5-2(1)}
\begin{proof}
I didn't have time to do all of these problems, since this week we have a midterm in this class and another class, in addition to the regular work which I can barely keep up with. 
\end{proof}


\end{enumerate}

%\pagebreak
\textbf{Problems from the PDF}

\textbf{Assignment 6}

\begin{enumerate}
\setcounter{enumi}{1}
\item This problem is based on the scaling. 
	\begin{enumerate}[label=(\alph*)]
	\item Let for some $1\leq p\leq \infty$ the inequality (Sobolev inequality)
	$$\norm{u}_p\leq C(n,p)\norm{\nabla u}_1
	$$
	hold for all $u\in C_0^\infty(\R^n), n\geq2$, with the constant $C$ independent of $u$. What are the possible values (the \textit{necessary} conditions) of $p$?
	\begin{proof}
	For all $\lambda> 0$, let $u_\lambda:= u\left(\frac{x}{\lambda}\right)$. Now $u_\lambda\in C^\infty_0$, so the Sobolev inequality holds for $u_\lambda$. Consider the right hand side, 
	\begin{align*}
	\norm{\nabla u}_1 
	&= \int \abs{\nabla\left[u\left(\tfrac{x}{\lambda}\right)\right]}\dx \\
	&= \int \frac{1}{\lambda}\abs{\left(\nabla u\right)\left(\tfrac{x}{\lambda}\right)}\dx &&\text{ by the chain rule}\\
	&= \lambda^{n-1}\int \abs{\left(\nabla u\right)\left(x\right)}\dx &&\text{ by change of variables}\\
	&= \lambda^{n-1}\norm{\nabla u}_1.
	\end{align*}
	Now consider the left hand side,
	\begin{align*}
	\norm{u_\lambda}_p &= \left(\int_{R^n}\abs{u\left(\tfrac{x}{\lambda}\right)}^p\dx\right)^{1/p} \\
	&= \left(\lambda^{n}\int_{R^n}\abs{u\left(x\right)}^p\dx\right)^{1/p} &&\text{ by change of variables}\\
	&= \lambda^{\sfrac{n}{p}}\left(\int_{R^n}\abs{u\left(x\right)}^p\dx\right)^{1/p}\\
	&= \lambda^{\sfrac{n}{p}} \norm{u}_p.
	\end{align*}
	Substituting and collecting $\lambda$ on the left side gives 
	$$\lambda^{\frac{n}{p}-n+1}\norm{u}_p \leq C\norm{\nabla u}_1,
	$$
	and this is true for all $\lambda>0$, even while the right hand side is finite and constant with respect to $\lambda$. Thus 
	$$\tfrac{n}{p}-n+1\leq 0,	$$
	otherwise $\lambda^{\frac{n}{p}-n+1}\norm{u}_p\to\infty$ as $\lambda\to\infty$. However we also have that 
	$$\tfrac{n}{p}-n+1\geq 0,	$$
	otherwise $\lambda^{\frac{n}{p}-n+1}\norm{u}_p\to\infty$ as $\lambda\to0$.
	Thus $\tfrac{n}{p}-n+1= 0,	$ so $p=\frac{n}{n-1}=n'$. \qedwhitehere
	\end{proof}
	
%	\pagebreak
	\item \mbox{}\vspace*{-22pt}
	\jpg{width=0.99\linewidth}{hw6-pdf2-b}
	\begin{proof}
	Suppose that $u\in C^1(B_r)$ for $r>0$, and let $\rho:\R^n\to\R^n$ be the function which scales by $r$, that is $r(x)=rx$. Notice that $u\circ \rho \in C^1(B_1)$. Thus 
	\begin{align*}
	\sup_{x,y\in B_{r/2}}\abs{u(x)-u(y)}
	&=\sup_{x,y\in B_{1/2}}\abs{u(rx)-u(ry)} \\
	&=\sup_{x,y\in B_{1/2}}\abs{(u\circ\rho)(x)-(u\circ \rho)(y)} \\
	&\leq C(n,p)\left(\int_{B_1}\big|\nabla (u\circ\rho)(x)\big|^p \dx \right)^{1/p} &&\text{by Morrey's inequality} \\
	&\leq C(n,p)\left(\int_{B_1}r^p\big|(\nabla u)(rx)\big|^p \dx \right)^{1/p} &&\text{by chain rule} \\
	&= C(n,p)r\left(\int_{B_1}\big|(\nabla u)(rx)\big|^p \dx \right)^{1/p}\\
	&= C(n,p)r^{1-n}\left(\int_{B_1}\abs{\nabla u(x)}^p \dx \right)^{1/p} && \text{by change of variables} 
	\end{align*}
	Thus $C(p,n,r)=C(n,p)r^{1-n}$. 
	\end{proof}
	\end{enumerate}

\end{enumerate}



\end{document}
