\documentclass[12pt]{article}

\usepackage{geometry,calc}
\usepackage{amsmath,amssymb,hyperref}

\def\quiztitle{Practice Problems 10}
\def\quizsubtitle{Math 4B,\qquad Spring 2017,\qquad Dr. Paul}
\pagestyle{empty}

\geometry{body={6.5in, 9in}, left=1in, top=1in}
\input{../../AxesFunction.tex}

\everymath{\displaystyle}

\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\vv}[2]{\begin{bmatrix} #1 \\ #2 \end{bmatrix}}
\newcommand{\vvv}[3]{\begin{bmatrix} #1 \\ #2 \\ #3\end{bmatrix}}
\newcommand{\vvvv}[4]{\begin{bmatrix} #1 \\ #2 \\ #3 \\ #4\end{bmatrix}}
\newcommand{\vvvvv}[5]{\begin{bmatrix} #1 \\ #2 \\ #3 \\ #4 \\ #5  \end{bmatrix}}

\begin{document}

%\hfill Student Name: \rule{2in}{.1pt}\\

%\hfill Section Time (e.g. 8am): \rule{2in}{.1pt}\\

\begin{center}
{\Huge \quiztitle}
\vskip.1in
{\large \quizsubtitle}
\end{center}

Practice problems are for your own benefit. You won't turn them in or have them graded, but I have the expectation that you have done these when I write my tests. You can check answers with a TA, in Math Lab, or with the professor.

\begin{enumerate}

\item Go back to the pendulum problem from class. Let $\gamma=2$, $k=10$.
 \begin{enumerate}
  \item Confirm that the equilibria are of the types claimed by doing the calculations in greater detail using the Jacobian matrix.
  \item Sketch the phase plane using the equilibrium types as your guide (you can compare your answer to the one in the textbook).
  \item Use Euler's Method to graph $\theta(t)$ if the pendulum has initial position $\theta=3\pi/4$ and initial velocity $\omega=0$. Sketch this solution on the phase plane.
  \item Use Euler's Method to graph $\theta(t)$ if the pendulum has initial position $\theta=0$, and initial velocity $\omega=3$. Sketch this solution on the phase plane.
  \item Use Euler's Method to graph $\theta(t)$ if the pendulum has initial position $\theta=0$, and initial velocity $\omega=10$. Sketch this solution on the phase plane. Interpret the results, and in particular the difference between this part and the previous one.
 \end{enumerate}
 
 \item Consider the system from class
  $$\begin{array}{ccl}
 x' & = & 4x+2y+2x^2-3y^2\\
 y' & = & 4x-3y+7xy
 \end{array}$$
 We showed that $(0,0)$ was a saddle.The other equilibria are
 $$(0.279,1.065),\quad (0.933,-1.057),\quad (-2.354,-0.483)$$
 Classify each of these using the Jacobian matrix at each point.
 
 \item Find and classify all equilibria for the system
 $$\begin{array}{ccl}
 x' & = & x-x^2-xy\\
 y' & = & 0.5y-0.75xy-0.25y^2
 \end{array}$$


\end{enumerate}

\end{document}