\documentclass[12pt]{article}

\usepackage{geometry,calc}
\usepackage{amsmath,amssymb,hyperref}

\def\quiztitle{Practice Problems 7}
\def\quizsubtitle{Math 4B,\qquad Spring 2017,\qquad Dr. Paul}
\pagestyle{empty}

\geometry{body={6.5in, 9in}, left=1in, top=1in}
\input{../../AxesFunction.tex}

\everymath{\displaystyle}

\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\vv}[2]{\begin{bmatrix} #1 \\ #2 \end{bmatrix}}
\newcommand{\vvv}[3]{\begin{bmatrix} #1 \\ #2 \\ #3\end{bmatrix}}
\newcommand{\vvvv}[4]{\begin{bmatrix} #1 \\ #2 \\ #3 \\ #4\end{bmatrix}}
\newcommand{\vvvvv}[5]{\begin{bmatrix} #1 \\ #2 \\ #3 \\ #4 \\ #5  \end{bmatrix}}

\begin{document}

%\hfill Student Name: \rule{2in}{.1pt}\\

%\hfill Section Time (e.g. 8am): \rule{2in}{.1pt}\\

\begin{center}
{\Huge \quiztitle}
\vskip.1in
{\large \quizsubtitle}
\end{center}

Practice problems are for your own benefit. You won't turn them in or have them graded, but I have the expectation that you have done these when I write my tests. You can check answers with a TA, in Math Lab, or with the professor.

\begin{enumerate}

 \item Consider the following system:
 $$\frac{dx}{dt}=(y-x)(1-x-y),\quad \frac{dy}{dt}=x(2+y)$$
 \be
  \item Find the critical points of the system
  \item Under what circumstances is $x$ increasing? Shade this region in the phase plane.
  \item Under what circumstances is $y$ increasing? Shade this region in the phase plane.
  \item Give a rough sketch of the vector field in the phase plane, and sketch some solution curves.
 \ee
 
\item Consider the system
  $$\vec x\,'(t)=\begin{bmatrix}1 & 1 \\ -2 & 4 \end{bmatrix}\vec x(t)$$
  \be
   \item Find the general solution.
   \item Solve the initial value problem with $x(0)=2$, $y(0)=4$.
  \ee
  
\item Do the following for the system
 $$\vec x\,'=\begin{bmatrix}2&3\\4&1\end{bmatrix}\vec x$$
 \be 
  \item Characterize the circumstances where $x$ is increasing/decreasing, and where $y$ is increasing/decreasing.
  \item At which points in the phase plane will the vectors be pointing directly towards the origin? Directly away from the origin?
  \item Sketch a phase portrait.
 \ee
 
 \item Find the general solutions for the following systems.
 \be
  \item $x'=x+y,\quad y'=-2x+4y$.
  \item $\vec x\,'=\begin{bmatrix} -1 & 1 \\ 1 & -1 \end{bmatrix}\vec x$
  \item $\vvv{x'}{y'}{z'}=\begin{bmatrix} -2 & 1 & 1 \\ 1 & -2 & 1 \\ 1 & 1 & -2\end{bmatrix}\vvv xyz$
 \ee

\item Which of the systems from the previous problem models a closed system with two water tanks exchanging water?\\
 
 \setlength{\unitlength}{1cm}
 \begin{picture}(6,5)
  \thicklines
  \put(0,0){\line(0,1){5}}
  \put(0,0){\line(1,0){2}}
  \put(0,5){\line(1,0){2}}
  \put(2,0){\line(0,1){1}}
  \put(2,1){\line(1,0){2}}
  \put(4,1){\line(0,-1){1}}
  \put(4,0){\line(1,0){2}}
  \put(6,0){\line(0,1){5}}
  \put(6,5){\line(-1,0){2}}
  \put(4,5){\line(0,-1){1}}
  \put(4,4){\line(-1,0){2}}
  \put(2,5){\line(0,-1){1}}
  \put(2,1.5){\line(1,0){2}}
  \put(2,3.5){\line(1,0){2}}
  \put(2,1.5){\line(0,1){2}}
  \put(4,1.5){\line(0,1){2}}
  \put(1,2.5){A}
  \put(5,2.5){B}
  \put(2.25,1.25){\vector(1,0){1.5}}
  \put(3.75,3.75){\vector(-1,0){1.5}}
 \end{picture}
 
 Sketch its phase portrait and write a few sentences interpreting the ``real-world'' implications of the solutions.

  
 \end{enumerate}

\end{document}