\documentclass[12pt]{article}

\usepackage{geometry,calc}
\usepackage{amsmath,amssymb,hyperref}

\def\quiztitle{Practice Problems 4}
\def\quizsubtitle{Math 4B,\qquad Spring 2017,\qquad Dr. Paul}
\pagestyle{empty}

\geometry{body={6.5in, 9in}, left=1in, top=1in}
\input{../../AxesFunction.tex}

\everymath{\displaystyle}

\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\begin{document}

%\hfill Student Name: \rule{2in}{.1pt}\\

%\hfill Section Time (e.g. 8am): \rule{2in}{.1pt}\\

\begin{center}
{\Huge \quiztitle}
\vskip.1in
{\large \quizsubtitle}
\end{center}

Practice problems are for your own benefit. You won't turn them in or have them graded, but I have the expectation that you have done these when I write my tests. You can check answers with a TA, in Math Lab, or with the professor.

\begin{enumerate}

 \item Work through the details of our in-class derivation of the logistic equation.

 \item A Chipotle sofritas burrito's temperature will change at a rate of 10\% of the difference between its temperature and the temperature of its surrounding per minute.
 
 Such a burrito is placed in an oven, which is also at $70^\circ$F initially, but then the temperature of the oven increases by $20^\circ$F per minute for the first 10 minutes, then remains at a constant temperature of $270^\circ$F for an additional 10 minutes. After this, the burrito is taken out of the oven, and left on the counter in a $70^\circ$ room for 5 minutes to cool.
 \begin{enumerate}
  \item Write down a differential equation modeling the burrito's temperature.
  \item Along what interval does the existence and uniqueness theorem guarantee that there a unique solution to the initial value problem in which the burrito's initial temperature is $50^\circ$F?
  \item If the burrito's initial temperature is $50^\circ$, find the burrito's final temperature, and sketch a graph of the burrito's temperature as a function of time.
 \end{enumerate}
  
  
  \item Consider the differential equation $x\frac{dy}{dx}=2y$. Consider solutions of the form $y=Cx^2$ and variations as possible solutions (there may be others!). Is there one, more than one, or no solution(s) with the following initial conditions:
 \be
  \item $y(0)=1$
  \item $y(0)=0$
  \item $y(-1)=1$
 \ee
 
 \item On what interval can we be sure there is a unique solution to the initial value problem
 $$y'=\sqrt x+\frac{y}{x-3},\quad y(1)=1$$
 
 \item On what interval can we be sure there is a unique solution to the initial value problem
 $$y'=x^{2/3}+\frac{y}{x-3},\quad y(1)=1$$
 
 \item Solve the ODE $y'=\sqrt{x+y+1}$ using the substitution $v=x+y+1$.
 
 \item Solve the ODE by reducing the order: $xy''=y'$ with $v=y'$, $\frac{dv}{dx}=y''$.
 
 \item Solve the ODE by reducing the order: $y''=y(y')^3$ with $v=y'$, $\frac{dv}{dy}v=y''$.
 
 \item Solve the ODE by noticing that it is exact: $2x+3y+(3x+2y)y'=0$.
 
 \item Come up with a new example of an exact ODE.
 
 \end{enumerate}

\end{document}