\documentclass[12pt,letterpaper]{article}

\usepackage{fancyhdr,fancybox}
\usepackage{mathtools}

\input{tskpreamble_nothms} %find me at /home/trevor/texmf/tex/latex/tskpreamble_nothms.tex
\input{tsktheoremstyles}

%%
%% Page set-up:
%%
\pagestyle{empty}
\lhead{\textsc{201B - Real Analysis \\}} 
\rhead{\textsc{Harutyunyan, Winter 2020} \\ Trevor Klar}
%\chead{\Large\textbf{A New Integration Technique \\ }}
\renewcommand{\headrulewidth}{0pt}
%
\renewcommand{\footrulewidth}{0pt}
%\lfoot{
%Office: \quad \quad \, M 2-3 \, \, SH 6431x \\
%Math Lab: \, W 12-2 \, SH 1607
%}
%\rfoot{trevorklar@math.ucsb.edu}

\setlength{\parindent}{0in}
\setlength{\textwidth}{7in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\parskip}{.5\baselineskip}
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{9in}

\setlist[enumerate,1]{label=\textbf{\arabic*.}}

\renewcommand{\phi}{\varphi}
\renewcommand{\epsilon}{\varepsilon}

\begin{document}
\pagestyle{fancy}
\begin{center}
{\Large Final Exam}%=================UPDATE THIS=================%
\end{center}

\begin{enumerate}

\item Let the sequences $\{a_n\}, \{r_n\}\subset \R$ be such that 
$$\sum_{i=1}^\infty |a_n|<\infty.$$
Prove that the series 
$$\sum_{i=1}^\infty \frac{a_n}{\sqrt{\abs{x-r_n}}}$$
converges absolutely for almost every $x\in\R$. 

\begin{proof}
Let $\{a_n\}, \{r_n\}$ be given as above, and let $g_n(x)=\frac{1}{\sqrt{\abs{x-r_n}}}$. We will show that the integral 
$$\int_{\alpha}^{\alpha+2} \sum_{n=1}^\infty {a_n}\,g_n(x)\dx$$
is finite over any region of length 2,\footnote{That is, for any $\alpha\in\R$.} which means the series is infinite on a set of measure 0.

First note that for any fixed $n$, 
$$\int_{\alpha}^{\alpha+2} g_n\dx = \int_{\alpha}^{\alpha+2} (x-r_n)^{-\sfrac{1}{2}} \dx= \frac{2(\alpha+2-r_n)}{\sqrt{\abs{\alpha+2-r_n}}} - \frac{2(\alpha-r)}{\sqrt{\abs{\alpha-r}}},$$
and by differentiating with respect to $\alpha$ we find that this value is greatest when 
$$0=\frac{1}{\sqrt{\abs{\alpha-r_n-2}}} - \frac{1}{\sqrt{\abs{\alpha-r_n}}},$$
which is to say that $\alpha-r_n=1$. Thus we conclude that 
$$\int_{\alpha}^{\alpha+2} g_n\dx\leq \int_{r_n-1}^{r_n+1} g_n\dx=\int_{-1}^1\frac{1}{\sqrt{t}}\dt =4 $$ for all $\alpha\in\R$ and all $ n\in\N$. 

To finish the proof, observe that 
$$\int_{\alpha}^{\alpha+2} \sum_{n=1}^\infty \frac{|a_n|}{\sqrt{\abs{x-r_n}}}\dx 
= \sum_{n=1}^\infty \int_{\alpha}^{\alpha+2} {|a_n|}\,g_n(x)\dx
= \sum_{n=1}^\infty {|a_n|} \int_{\alpha}^{\alpha+2}  g_n(x)\dx
%\leq \left(\sum_{n=1}^\infty {|a_n|}\right)(4)
\leq 4\sum_{n=1}^\infty {|a_n|}
$$
which is finite. Since the series is infinite only on a zero-measure subset of an arbitrary interval of length 2, then the union of all such subsets also has measure zero, and we're done. 
\end{proof}

\pagebreak
\item Suppose $f\in L^1[0,1]^2$ with respect to two dimensional Lebesgue measure $\mu$. Prove that if 
$$\int_{[0,a],[0,b]} f \der\mu = 0$$
for all $(a,b)\in [0,1]^2$, then $f=0$ \muae{} in $[0,1]^2$. 

\begin{proof}Since we can decompose $f$ as $f=f^+-f^-$, then 
$$f(x)=0\iff f^+(x)=f^-(x)=0$$ 
so \Wlog{} suppose $f$ is nonnegative.

($\int_R=0$) Observe that the integral over any rectangle
\begin{align*}
\int_{[a,b]\times[c,d]}  f\der\mu
&= \int_{[0,b]\times[0,d]}  f\der\mu 
	- \int_{[0,a]\times[0,d]}  f\der\mu 
	- \int_{[0,b]\times[0,c]}  f\der\mu 
	+ \int_{[0,a]\times[0,c]}  f\der\mu \\
&= 0-0-0+0.
\end{align*}
%and note that any two rectangles intersect in a rectangle, 

($\int_U=0$) Let $U$ be open. For each $n\in\N$, define a cover of $[0,1]^2$ by $2^{2n}$ squares of side length $2^{-n}$ and denote it $\{Q_n^i\}_{i=1}^\infty$. For any given $n$, there are finitely many $Q_n^i\subseteq U$, and so the union of all such is a countable union of cubes. To see that it covers $U$, let $(x,y)\in U$. Since $U$ is open, some neighborhood of $(x,y)$ is a subset of $U$, and certainly some sufficiently large $n$ gives a cube fully contained in that neighborhood which contains $n$\footnote{This can be made more rigorous, but this proof is getting absurdly long.}. Then 
$$\int_U f\der\mu = \sum_{i,n:Q_n^i\subseteq U} \int_{Q_n^i} f\der\mu = 0.$$

($\int_G=0$) Let $G$ be a $G_\delta$ set, so $G=\bigcap_{i=1}^\infty U_i$, where each $U_i$ is open. Then 
$$\int_G f\der\mu = 0$$
[I can't figure out how to prove this part.]

($\int_B=0$) Let $B$ be any Borel set in $[0,1]^2$. Since $\mu$ is Radon, then for each $n\in\N$ there exists an open set $U_n$ such that $B\subseteq U_n$ and $\mu(U_n\setminus B)<\frac{1}{n}$. Since $U_n$ is a decreasing sequence\footnote{Although $U_{n+1}$ is not necessarily a subset of $U_n$ by default, we know that they both contain $B$, and intersecting them yields $\tilde{U}_{n+1}=U_n \cap U_{n+1}$ so that $B\subset \tilde{U}_{n+1} \subset U_n$ and $\mu(\tilde{U}_{n+1}\setminus B)\leq \mu({U}_{n+1}\setminus B) < \frac{1}{n}$. Starting with $\tilde{U}_1=U_1$ and constructing the rest inductively yields the desired $\{\tilde{U}_n\}_{n=1}^\infty$. We drop the $\sim$ notation above.}
of sets with $\mu(U_1)\leq\mu[0,1]^2=1<\infty,$  then $\mu(U)=\lim\limits_n(\mu(U-n))$ where $U=\bigcap\limits_n U_n$. Thus 
\begin{align*}
B&\subset U, \\
\text{and } \mu(U\setminus B)&< \frac{1}{n} \; \forall n, \\
\text{so } \mu(U\setminus B)&=0.
\end{align*}
Therefore 
\begin{align*}
\int_B f\der\mu &= \int_U f\der\mu - \int_{U\setminus B} f\der\mu \\
&= \int_U f\der\mu \\
&=0 \text{ since }U\text{ is }G_\delta.
\end{align*}

($\int_A = 0$) Let $A=\{(x,y)\in[0,1]^2 : f(x,y)>0\}$, and suppose for contradiction that $\mu(A)>0$. This gives us that 
$$\int_A f \der\mu >0.$$
Since $\mu$ is Borel-regular, there exists a Borel set $B\supset A$ such that $\mu(B)=\mu(A)$. This means that $\mu(B\setminus A)=0$. Therefore 
\begin{align*}
\int_A f\der\mu &= \int_B f\der\mu - \int_{B\setminus A} f\der\mu \\
&= \int_B f\der\mu \\
&=0 \quad\quad\quad\quad\text{since $B$ is Borel.}
\end{align*}
This contradicts that $\int_A f\der\mu>0$, and so we conclude that $\mu(A)=0$. 
\end{proof}

\pagebreak
\item Let $A \subset X$ be a closed subspace of of a Banach space $X$ and let $k\in X$ be fixed. Is the distance 
$$\dist{k}{A}=\inf\{\norm{k-a} \;:\; a\in A\}$$
attained? 

\answer No. As a counterexample, let $X=\ell_\infty$, the space of all bounded sequences of real numbers, with norm $\norm{x}=\sup\limits_n \abs{x_n}$. Let 
\[\begin{array}{rcllll}
k&= &2, &2, &2, &2, \dots \\
a_1&= &0.9, &2, &2, &2, \dots \\ 
a_2&= &2, &0.99, &2, &2, \dots \\ 
a_3&= &2, &2, &0.999, &2, \dots \\ 
&\vdots
\end{array}\]
Observe that $A=\{a_n : n\in \N\}$ is closed, since it has no accumulation points: For any $n,m\in\N$, 
\begin{align*}
\norm{a_n-a_m}&=\norm{\big(0,0,\dots,0, (1+10^{-n}), 0, \dots, 0, (1+10^{-m}), 0, 0, \dots\big)} \\
&= \max\{(1+10^{-n}), (1+10^{-m})\} \\
&\geq1.
\end{align*}
Next note that for every $a_n$ the distance $\norm{k-a_n}=1+10^{-n}$, but
\begin{align*}
\dist{k}{A}
&=\inf\limits_n\norm{k-a_n} \\
&=\inf\limits_n\{1+10^{-n}\} \\
&=1,
\end{align*}
so $\dist{k}{A}$ is never attained. \qed
\end{enumerate}

\end{document}
