\documentclass[a4paper,12pt]{article}
\usepackage{amssymb,amsmath,amsthm}
\usepackage[tmargin=1.5in,bmargin=1.5in]{geometry}
\usepackage{graphicx}

\parindent=0in
\setlength{\parskip}{1em}

\geometry{
  body={7in, 10in},
  left=0.5in,
  top=0.75in
}
\pagestyle{empty}

\begin{document}

\begin{center} {\Large \scshape Math 34A Course Information}
\end{center}

\vspace{0.75cm}

\begin{itemize}
\item {\bf Course:} Math 34B, Summer 2022
\item {\bf Instructor:} Trevor Klar,  trevorklar@math.ucsb.edu
\item {\bf Teaching Assistant:} Alfredo Ramirez
\item {\bf Lecture:} M T W R, 12:30-1:35 Ellison Hall 2626
\item {\bf Text:} UCSB's custom-printed book for this course: Calculus and Mathematical Reasoning for Social and Life Sciences (Cooper), now available free online!
\item {\bf Office Location:} South Hall 6431X (Grad Tower, 6th floor, blue side, first door on the right)
\end{itemize}

\paragraph{Grading}
The grading scheme is as follows:
\begin{center}
\begin{tabular}{lll}
Homework       & 20\% & due after every class before 11:00PM \\
Quizzes        & 10\% & weekly in section  \\ 
Midterm Exams & 40\% & 1st Midterm is \_\_\_day, June \_\_ in class \\
Final Exam  & 30\% & Tuesday, June 7 at 4:00PM
\end{tabular}
\end{center}
Letter grades are determined using a standard 10-point scale, uncurved.

\paragraph{Homework}
 The lectures are meant to be a supplement to the book, not a replacement. Please read the book as we go along. Homework will be due on class days before the end of the day. 
 
 \paragraph{Quizzes} 
 There will be a quiz in every section meeting (10 in total) based on the material learned so far (including review topics). The quizzes are designed to be a short checkup of how you're doing so far; they'll give you early feedback about how effective your studying methods are so far. If you're struggling, \textit{get help!}
 
 \paragraph{Exams} 
 Late homework will not be accepted except in the case of a medical emergency when a doctor's note can be provided. 




\paragraph{Resources}
\begin{itemize}
\item Instructor office hours (posted on Gauchospace)
\item TA office hours (posted on Gauchospace)
\item Math Lab: M-F, 12-5PM in South Hall
\item CLAS : Registration and schedules available at http://clas.sa.ucsb.edu/
\end{itemize} 



\end{document}
