\documentclass[12pt,letterpaper]{article}

\usepackage{fancyhdr,fancybox}
\usepackage{wrapfig}

\input{tskpreamble_nothms} %find me at /home/trevor/texmf/tex/latex/tskpreamble_nothms.tex
\input{tsktheoremstyles}

%%
%% Page set-up:
%%
\pagestyle{empty}
\lhead{\textsc{221 - Topology} \\ }
\rhead{\textsc{McCammond, Winter 2019} \\ Trevor Klar}
%\chead{\Large\textbf{A New Integration Technique \\ }}
\renewcommand{\headrulewidth}{0pt}
%
\renewcommand{\footrulewidth}{0pt}

\setlength{\parindent}{0in}
\setlength{\textwidth}{7in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\parskip}{.5\baselineskip}
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{9in}

\setlist[enumerate,1]{label=\textbf{\arabic*.}}

\renewcommand{\inv}[1]{\overline{#1}}

\begin{document}
\pagestyle{fancy}
\begin{center}
{\Large Homework 6}%===============UPDATE THIS===============%
\end{center}

\begin{enumerate}

\setcounter{enumi}{7}
\item Does the Borsuk-Ulam Theorem hold for the torus? In other words, for every map $f:S^1\times S^1\to \R^2$ must there exist $(x,y)\in S^1\times S^1$ such that $f(x,y)=f(-x,-y)$?

\answer No. Consider $f(x,y)=(\cos x, \sin x)$. This is clearly a map since it is constant with respect to $y$ and it is the inclusion map with respect to $x$, but $f$ never vanishes and is odd, so $f(x,y)\neq f(-x,-y)$ for all $(x,y)$. \qed

\setcounter{enumi}{9}
\item From the isomorphism $\pi_1\big((X\times Y),(x_0,y_0)\big)\approx \pi_1(X,x_0)\times \pi_1(Y,y_0)$ it follows that loops in $X\times	\{y_0\}$ and $\{x_0\times Y\}$ represent commuting elements of $\pi_1\big((X\times Y),(x_0,y_0)\big)$. Construct an explicit homotopy demonstrating this. 

\answer Let 
\begin{itemize}
\item $\gamma=\big(\tilde{\gamma}(s),y_0\big)$, where $\tilde{\gamma}$ is a loop in $(X,x_0)$. 
\item $\eta=\big(x_0,\tilde{\eta}(s)\big)$ where $\tilde{\eta}$ is a loop in $(Y,y_0)$. 
\item For any loop $\alpha$ in any space, let $\omega_t\sqcdot\alpha$ denote a reparametrization of $\alpha$ which is constant for $s\in [0,t]$, then does $\alpha$ over the remaining $s$-values in $[0,1]$. Define $\alpha\sqcdot\omega_t$ similarly except do $\alpha$ first, then wait. 
\end{itemize}
Observe that 
\begin{align*}
\gamma\sqcdot\eta&=(\tilde{\gamma}\sqcdot\omega_{\sfrac{1}{2}}\,\,,\, \omega_{\sfrac{1}{2}}\sqcdot\tilde{\eta})\\
\eta\sqcdot\gamma&=(\omega_{\sfrac{1}{2}}\sqcdot\tilde{\gamma}\,\,,\, \tilde{\eta}\sqcdot\omega_{\sfrac{1}{2}}),
\end{align*}
so 
$$f_t=(\omega_{\sfrac{t}{2}}\sqcdot\tilde{\gamma}\sqcdot\omega_{1-\sfrac{t}{2}}\,\,,\, \omega_{1-\sfrac{t}{2}}\sqcdot\tilde{\eta}\sqcdot\omega_{\sfrac{t}{2}})$$
is the desired homotopy. \qed

\end{enumerate}
\jpg{width=\textwidth}{hw6-p15-1}
\begin{enumerate}
\item[]
\begin{proof}
Let $\gamma$ be a loop based at $x_1$. Then 
$$\gamma\xmapsto{\quad\beta_h\quad}h\sqcdot\gamma\sqcdot\inv{h}\xmapsto{\quad f_*\quad}f(h\sqcdot \gamma\sqcdot \inv{h})=fh\sqcdot f\gamma\sqcdot f\inv{h}$$
and 
$$\gamma\xmapsto{\quad f_*\quad} f\gamma \xmapsto{\quad\beta_{fh}\quad}fh\sqcdot f\gamma\sqcdot \overline{fh}=fh\sqcdot f\gamma\sqcdot f\inv{h},$$
so the diagram commutes.
\end{proof}

\pagebreak
\setcounter{enumi}{15}
\item Show that there are no retractions $r:X\to A$ in the following cases:
	\begin{enumerate}[label=(\alph*)]
	\item $X=\R^3$ with $A$ any subspace homeomorphic to $S^1$. 
	\begin{proof}
	Suppose for contradiction there is a retraction $r:X\to A$, and let $\gamma$ be any loop in $A$, where $x_0$ denotes the basepoint. We know $\R^3$ is contractible, so by composing such a homotopy with $\gamma$ we can produce $f_t$, a straight-line homotopy in $\R^3$ from $\gamma$ to $x_0$. Then $r\circ f_t$ is a homotopy in $A$ from $\gamma$ to $x_0$, contradicting that $\pi_1(A)\neq0$. \qedwhitehere
	\end{proof}
	\item $X=S^1\times D^2$ with $A$ its boundary torus $S^1\times S^1$.
	\begin{proof}
	We know that $\pi_1(S^1\times S^1)=\Z\times\Z$, so any loop in $A$ is homotopic to a loop $(\omega_n, \gamma_m)$ for $n,m\in \Z$ which goes around the torus $n$ times in one direction and $m$ times in the the other.  Consider $(\omega_n, \gamma_m)\in X$, and note that $D^2$ is contractible, so there is a homotopy $f_t$ in $X$ between $(\omega_n, \gamma_m)$ and $(\omega_n, 0)$. Assuming a retraction $r:X\to A$ exists, we can compose $r\circ	f$ to find that $(\omega_n, \gamma_m)\simeq(\omega_n, x_0)$ in $A$, contradicting that $\pi_1(S^1\times S^1)\neq \Z\times 0$. \qedwhitehere
	\end{proof}
	\item $X=S^1\times D^2$ with $A$ the circle shown in the figure. 
	\begin{proof}
	We will use the fact that if $X$ retracts to $A$, then the inclusion map $A\hookrightarrow X$ induces an injection $\pi_1(A)\inj\pi_1(X)$ (and in fact, would have saved time by using it on parts (a) and (b) as well). Observe that the loop which traverses $A$ once is homotopic to $0$ in $X$ by the following homotopy: 
	\jpg{width=0.8\textwidth}{hw6-p16c-1}
	Thus $1\in\pi_1(A)\mapsto 0\in\pi_1(X)$, so the kernel is nontrivial, and the homomorphism is not injective. 
	\qedwhitehere
	\end{proof}
	\item $X=D^2\wedgeprod D^2$ with $A$ its boundary $S^1\wedgeprod S^1$.
	\begin{proof}
	We know that $\pi_1(X)=0$ since $X$ is contractible and $\pi_1(A)$ is the free group on two generators, so any homomorphism from $\pi_1(A)\to\pi_1(X)$ fails to be injective since everything maps to zero. 
	\end{proof}
	\item $X$ a disk with two points on its boundary identified and $A$ its boundary $S^1\wedgeprod S^1$.
	\begin{proof}
	If $g,f$ are the generators of $\pi_1(A)$, then $g\inv{f}$ is a nonzero element in $\pi_1(A)$ which maps to $0\in \pi_1(X)$ under the homomorphism induced by the inclusion:
	\jpg{width=0.5\textwidth}{hw6-p16e-1}
	so the homomorphism is not injective. \qedwhitehere
	\end{proof}
	\item $X$ the M\"obius band and $A$ its boundary circle. 
	\begin{proof}
	I can't figure this out. $X$ deformation retracts to its central circle, so $\pi_1(X)=\Z$, but also $A$ is a circle, so $\pi_1(A)=\Z$ as well. I can't come up with any reason why $\iota^*$ would fail to be injective either, since we can't homotope a nontrivial loop in the boundary to a constant loop in $X$ in any obvious way. In fact, it seems to me that $\iota^*(n)=2n$, which \emph{is }injective. 
	\end{proof}
	\end{enumerate}

\item Construct infinitely many nonhomotopic retractions $S^1\wedgeprod S^1\to S^1$. 

\answer Denote points in $S^1\wedgeprod S^1$ by $\theta\in(0,4\pi)$, so that $(0,2\pi]$ represents a point in the first circle, $[2\pi,4\pi)$ represents a point in the second circle, and $2\pi$ is in both circles. Then define 
\[
r_n(\theta)=\begin{cases}
\theta, &\theta \in (0,2\pi] \\
n\theta, &\theta \in [2\pi,4\pi)
\end{cases}
\]
where we make the usual identification in the codomain that $\theta\sim 2n\pi \,\,\forall n\in \N$. It is clear that these are nonhomotopic maps since they are loops in distinct equivalence classes of $\pi_1(S^1)$. 
\item 
Using Lemma 1.15, show that if a space $X$ is obtained from a path-connected subspace $A$ by attaching a cell $e^n$ with $n\geq 2$, then the inclusion $A\hookrightarrow X$ induces a surjection on $\pi_1$. Use this to show:
	\begin{enumerate}
	\item The wedge sum $S^1\wedgeprod S^2$ has fundamental group $\Z$. 
	\item For a path-connected CW complex $X$ the inclusion map $X^1\hookrightarrow X$ of its 1-skeleton induces a surjection $\pi_1(X^1)\to \pi_1(X)$. [For the case that $X$ has infinitely many cels, see Proposition A.1 in the appendix.]
	\end{enumerate}
\begin{proof}Consider $X$ as the union of $A_\epsilon$ and $e^n_\epsilon$, which are $\epsilon$-neighborhoods of $A$ and $e^n$ respectively in $X$. Since $A,e^n$ are deformation retractions of $A_\epsilon, e^n_\epsilon$, it suffices to show that the property holds for those subspaces. 
\jpg{width=0.8\textwidth}{hw6-p18-1}
For path-connected spaces, we know that $\pi_1$ is independent of base point, and $A$ and $e^n$ are both path-connected, which means $X$ is as well. Thus \Wlog{} we can suppose the basepoint $x_0\in(A_\epsilon\cap e^n_\epsilon)$. Given any loop $f$ in $X$, we can use Lemma 1.15 to write it as $f=\left(\bigsqcdot_{i=1}^n \gamma_i\right)$, where each $\gamma_i$ is in $A_\epsilon$ or $e^n_\epsilon$. Let 
$$E=\{i:\gamma_i\in e^n_\epsilon\}.$$
Since $e^n_\epsilon$ is contractible, then for each ${\gamma_i}$ such that ${i\in E}$, $\gamma_i\simeq\id$, so 
$$f=\left(
%\overset{n}{\underset{i=1}{\bigsqcdot}}
\bigsqcdot_{i=1}^n
\gamma_i\right)\simeq \left(\bigsqcdot_{i\in E^\complement} \gamma_i\right)$$
which is a loop in $A_\epsilon$. 

Thus for every loop in $X$, there is a homotopy equivalent loop in $A$, which means $\pi_1(X)$ is a subgroup of $\pi_1(A)$ (up to isomorphism). 
\qedwhitehere 
\end{proof}
\begin{proof}(i)
It suffices to show that the inclusion $S^1\hookrightarrow S^1\wedgeprod S^2$ induces an injective homomorphism $\pi_1(S^1)\to\pi_1(S^1\wedgeprod S^2)$, since it is already surjective by above. For any loop $\gamma\in S^1$ such that $\gamma\not\simeq c$ where $c$ is the constant loop, consider $\gamma\in (S^1\wedgeprod S^2)$. Call the intersection point of the wedge $x_0$, and \Wlog{} suppose $x_0$ is the basepoint. Suppose there is a homotopy $f_t$ of loops in $(S^1\wedgeprod S^2)$ such that $f_0=\gamma$ and $f_1=c$.  Since any loop with points in $S^1-\{x_0\}$ and $S^2-\{x_0\}$ must pass through $\{x_0\}$, then at every time $t$, $f_t$ is a concatenation of loops in $S^1$ with loops in $S^2$. Then we can write $F$ as a concatenation of homotopies 
$$f_t=\left(\bigsqcdot_{i=1}^n f_{i,t}\right). $$
Since $f_1=c$, then $f_{i,1}=c$ for all $i$, which means that if $f_{j,0}$ is any of the loops in $S^1$, then $f_{j,t}$ is a homotopy between that loop and $c$ ion $S^1$, contradicting that $\gamma\not\simeq c$. \qedwhitehere
\end{proof}
\begin{proof}(ii)
Inductively, we can see that 
$$\pi_1(X^1)\surj \pi_1(X^2)$$ 
since $X^2$ is exactly $X^1$ with 2-cells attached, and 
$$\pi_1(X^1)\surj \pi_1(X^n)\implies \pi_1(X^1)\surj \pi_1(X^{n+1})$$ 
since $X^n$ is exactly $X^{n+1}$ with $(n+1)$-cells attached. Thus the map is surjective for finite-dimensional CW complexes. 

Proposition A.1 shows that a compact subspace of a CW complex is contained in a finite subcomplex. This means that for an arbitrary curve $\gamma\in X^\infty$, the image of the curve is compact since $I$ is compact, so it is contained in $X^n$ for some $n$. Thus there is some $\gamma'\in X^n$ with $\gamma'\simeq\gamma	$ and we are done. 
\end{proof}
\end{enumerate}
\vfill

Collaborators:
\begin{enumerate}
\item[] None for this homework.
\end{enumerate}
\end{document}



