\documentclass[12pt,letterpaper]{article}

\usepackage{fancyhdr,fancybox}
\usepackage{wrapfig}

\input{tskpreamble_nothms} %find me at /home/trevor/texmf/tex/latex/tskpreamble_nothms.tex
\input{tsktheoremstyles}

%%
%% Page set-up:
%%
\pagestyle{empty}
\lhead{\textsc{221 - Topology} \\ }
\rhead{\textsc{McCammond, Winter 2019} \\ Trevor Klar}
%\chead{\Large\textbf{A New Integration Technique \\ }}
\renewcommand{\headrulewidth}{0pt}
%
\renewcommand{\footrulewidth}{0pt}

\setlength{\parindent}{0in}
\setlength{\textwidth}{7in}
\setlength{\evensidemargin}{-0.25in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\parskip}{.5\baselineskip}
\setlength{\topmargin}{-0.5in}
\setlength{\textheight}{9in}

\setlist[enumerate,1]{label=\textbf{\arabic*.}}

\renewcommand{\inv}[1]{\overline{#1}}

\begin{document}
\pagestyle{fancy}
\begin{center}
{\Large Homework 7}%===============UPDATE THIS===============%
\end{center}

\begin{enumerate}


\item Show that (i) the free product $G*H$ of nontrivial groups $G$ and $H$ has trivial center, and (ii) the only elements of $G*H$ of finite order are conjugates of finite-order elements of $G$ and $H$. 
\begin{proof}(i)
Let $g\in G$, $h\in H$. If $z$ is in the center of $G*H$, then $zg=gz$ which means that $z$ is either $g, g^{-1},$ or the empty word $[e]$. Similarly, $zh=hz$ which means that $z$ is either $h, h^{-1},$ or $[e]$. Thus if $G,H$ are nontrivial then for nontrivial $g,h$ we have $g\neq g^{-1}\neq h\neq h^{-1}$, so $z$ must be $[e]$. 
\end{proof}
\begin{proof}(ii)
Let $x\in G*H$ with $x^n=[e]$. By simplifying, we can write $x$ as a word of alternating letters in $G$ and $H$, so $x=(g_1h_1g_2\dots g_{k-1}h_kg_k)$. Then for as many letters as possible (potentially none), we group the letters on the ends of the word which are inverses; i.e. 
\begin{align*}
x&=(g_1h_1)(g_2\dots g_{k-1})(h_kg_k)\\
x&=(g_1h_1)(g_2\dots g_{k-1})(h_1^{-1}g_1^{-1}).\\
x&=(g_1h_1)(z)(h_1^{-1}g_1^{-1}),\\
\end{align*}
where we let $z$ be the alternating word $(g_2\dots g_{k-1})$. Now we consider $x^n$. We know that everything must cancel, and the ends of course cancel, which means 
\begin{align*}
[e]&=x^n \\
&=(g_1h_1)(z)(h_1^{-1}g_1^{-1}) \, \, 
(g_1h_1)(z)(h_1^{-1}g_1^{-1}) \cdots
(g_1h_1)(z)(h_1^{-1}g_1^{-1})\\
&=(g_1h_1)(z)^n(h_1^{-1}g_1^{-1})\\
\end{align*}
which means that $z$ must be of order $n$. However, no  alternating word of $g$'s and $h$'s with length at least 2 is of finite order, since self-multiplying would just concatenate the same word with itself. Therefore $z$ must be a single letter of order $n$ in either $G$ or $H$, and $x$ is a conjugate of $z$. 
\end{proof}

\setcounter{enumi}{2}
\item Show that the complement of a finite set of points in $\R^n$ is simply connected if $n\geq3$. 
\begin{proof}
\WLOG{} Let $X=\R^n - \{\vec{x}_i\}_{i=1}^{k}$, with basepoint the origin. 

(i) To see that $X$ is path-connected, let $x\in X$. If $x $ is not a multiple of $ x_i$ for any $i$, then there is a straight-line path from $x$ to the origin. Otherwise suppose $x \parallel x_i$ for some $i$. Then choose a point $x'$ near $x$ such that $x $ is not a multiple of $ x_i$ for any $i$ (we know we can do this since there are infinitely many directions orthogonal to $x$ in which to find $x'$, and only infinitely many $x_i$), and there is a straight-line path from $x$ to $x$ to $0$. Thus for every $x\in X$ we have a path $\rho_x:I\to X$ connecting $x$ to $0$, so $X$ is path-connected.

(ii) To see that $\pi_1(X)=0$, observe that for any loop $\gamma$ in $X$, we can find a homotopy from $\gamma$ to the constant loop $0$ by using $\rho_x$. Let $R:X\times I \to X$ be given by $R(x,t)=\rho_x(t)$. Then $R(\gamma(s),t)$ is the desired homotopy. 
\end{proof}

\item Let $X\subset \R^3$ be the union of $n$ lines through the origin. Compute $\pi_1(\R^3 - X)$. We can deformation retract $X$ to a ball with $n$ lines missing, and since the origin is missing, we can deformation retract to a sphere with $2n$ antipodal points missing. 
\jpg{width=0.8\textwidth}{hw7-p4-1}
This sphere is diffeomorphic via spherical projection to a disk with $2n-1$ points missing, which deformation retracts to a wedge of $2n-1$ circles. Thus $\pi_1(\R^3-X)$ is the free group on $2n-1$ generators. \qed 

\setcounter{enumi}{6}
\item Let $X$ be the quotient space of $S^2$ obtained by identifying the north and south poles to a single point. Put a cell complex structure on $X$ and use it to compute $\pi_1(X)$. 

\answer First observe that $X$ the following shapes have the same homotopy type:
\jpg{width=0.8\textwidth}{hw7-p7-1}
The last figure is the same because the center disc is contractible, and modding it out yields the middle figure. It is on the last figure that we put a cell structure. $X$ has one 0-cell, two 1-cells and a 2-cell to form a torus, with one additional 2-cell attached spanning the center. We know that a torus has fundamental group $\Z\times	\Z$, and if we attach the additional 2-cell along the loop $(1,0)$, then 
$$\pi_1(X)=\quotient{\Z\times\Z}{\langle(1,0)\rangle}=\quotient{\Z\times\Z}{\Z}=\Z.$$
\qed 

\pagebreak
\item Compute the fundamental group of the space obtained from two tori $S^1\times S^1$ by identifying a circle $S^1\times \{x_0\}$ with the corresponding circle in the other torus. 

\answer We can put a cell structure on this space as a wedge of 3 circles $a,b,c$, with 2-cells attached along $ab\inv{a}\inv{b}$ and $ac\inv{a}\inv{c}$, respectively. 
\jpg{width=0.8\textwidth}{hw7-p8-1}
Thus $\pi_1(X)=\quotient{\bigop{*}\limits_{i=1}^3\Z_i}{\begin{array}{l}
aba^{-1}b^{-1} \\ aca^{-1}c^{-1}
\end{array} }$.
\qed 

Remark: Is the above notation equivalent to $\pi_1(X)=\langle a,b,c \mid ab=ba, ac=ca \rangle$? I'm not totally clear on how that notation works.

\setcounter{enumi}{16}
\item Show that $\pi_1(\R^2-\Q^2)$ is uncountable. 
\begin{proof}
Let $(\pi,0)$ be the basepoint. For every irrational number $\alpha$, let $\gamma_\alpha$ be the straight line path from $(\pi,0)$ to $(\pi,\pi)$ to $(\alpha,\pi)$ to $(\alpha, -\pi)$ to  $(\pi, -\pi)$ to $(\pi,0)$. 
\jpg{width=0.6\textwidth}{hw7-p17-1}
Clearly $\gamma_\alpha\not\simeq\gamma_\beta$ for $\alpha\neq\beta$, since any homotopy between the corresponding third segments of the paths would have to pass through points in $\Q^2$ as the $x$-coordinates moved from $\alpha$ to $\beta$. Thus we have an injective function from irrational numbers to loops in $\pi_1(X)$, so we're done. 
\end{proof}



\end{enumerate}
\vfill

Collaborators:
\begin{enumerate}
\item[] None for this homework.
\end{enumerate}
\end{document}



