\documentclass[letterpaper]{article}
%\documentclass[a5paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[letterpaper,top=1in,bottom=1in,left=1in,right=1in,marginparwidth=1.75cm]{geometry}
%\usepackage[a5paper,top=1cm,bottom=1cm,left=1cm,right=1.5cm,marginparwidth=1.75cm]{geometry}

\input{tskpreamble}

\pgfplotsset{compat=1.13}

\title{Math 501 \linebreak
Homework 1}
\author{Trevor Klar}

\begin{document}

\maketitle

\begin{enumerate}
\item For a set $A$, let $\{0,1\}^A$ be the set of all functions from $A$ to the two point set $\{0,1\}$. Prove that $|\{0,1\}^A|=|\powerset{A}|$.
\begin{proof}
Let $\Omega: \{0,1\}^A \to \powerset{A}$ be the following mapping: $$\Omega(f) = \{x \in A : f(x) = 1\}$$ This is to say that, for any function $f:A \to \{0,1\}$, where the set $S \subset A$  is the set such that $f(S)=\{1\}$, then $\Omega(f) = S$. 

\textbf{Claim:} $\Omega$ is a bijection, so $|\{0,1\}^A|=|\powerset{A}|$.

First, we will show that $\Omega$ is 1-1. Let $f,g:A \to \{0,1\}$ be two distinct functions. Since $f \neq g$, then there exists some $x \in A$ which maps to 1 under one function, and 0 under the other. Therefore, the set $\Omega(f) \neq \Omega(g)$, since $x$ is an element of one set, and not the other. Thus, $\Omega$ is 1-1.

Now, we will show that $\Omega$ is onto. Let $S$ be an arbitrary subset of $A$. Since the domain of $\Omega$ is $\{0,1\}^A$ (which is the set of \emph{all} functions from $A$ to $\{0,1\}$), then there exists a function $f \in \domain{\Omega}$ such that $f(S)=\{1\}$, and $f(A-S)=\{0\}$. This means that $\Omega(f)=S$, and therefore, $\Omega$ is onto.
\end{proof}

\item Prove that there is no function from a set $A$ onto $\{0,1\}^A$. 
\begin{proof}
Let $\Phi$ be a function from $A$ to $\{0,1\}^A$, and let $a$ be an arbitrary element of $A$. Then, there exist functions $f_{a_0},f_{a_1} \in \{0,1\}^A$ such that 
\[
\begin{array}{cc}
{
f_{a_0}(x)=
\begin{cases}
0 & x=a\\
1 & x\neq a \\
\end{cases}
\quad

} & {

\quad
f_{a_1}(x)=
\begin{cases}
1 & x=a\\
0 & x\neq a \\
\end{cases}
}
\end{array}
\]
This means that for every $x \in A$; $\Phi(x)$ can be either $f_{x_0}$, or $f_{x_1}$, (or neither), but not both. Therefore, whenever $\Phi$ maps an element of $A$ to a function in $\{0,1\}^A$, it always leaves at least one other function behind. Thus, $\Phi$ is not onto. 
\end{proof}

\item Let $f:X \to Y$ be a function bewteen sets $X$ and $Y$. 
\begin{enumerate}[label=(\alph*)]
\item Suppose $A \subset X$. Prove that $A \subset f^{-1}(f(A))$.
\begin{proof}
Let $x$ be an arbitrary element of $A$. Since $x \in \domain{f}$, there exists some $y \in Y$ such that $f(x)=y$. Consider the preimage of $y$; $f^{-1}(\{y\})$. Since $f(x)=y$, then $x \in f^{-1}(\{y\})$, by definition. Also, since $x \in A$ and $f(x)=y$, then $\{y\} \subset f(A)$. Therefore, $x \in f^{-1}(\{y\}) \subset f^{-1}(f(A)).$
\end{proof}
\pagebreak
\item Give an example to show $f^{-1}(f(A)) \not\subset A$.
\begin{example*} Consider the following function, $f:\{1,2,3,4\} \to \{5,6,7\}$, whose definition is given by the following figure:
\begin{center}
\begin{tikzpicture}
%put some nodes on the left
\foreach \x in {1,2,3,4}{
\node[inner sep=2pt] (d\x) at (0,5-\x) {\x};
}
\node[fit=(d1) (d2) (d3) (d4),ellipse,draw,minimum width=1cm] {}; 
%put some nodes on the center
\foreach \x[count=\xi] in {5,6,...,7}{
\node[inner sep=2pt] (r\xi) at (2,8.5-\x) {\x};
}
\node[fit=(r1) (r2) (r3),ellipse,draw,minimum width=1.5cm] {}; 
%put some nodes on the right
\draw[-latex] (d1) -- (r1);
\draw[-latex] (d2) -- (r1);
\draw[-latex] (d3) -- (r2);
\draw[-latex] (d4) -- (r3);
\end{tikzpicture}
\end{center}
Let $A=\{2,3,4\}$. According to the figure above, $f(A)=\{5,6,7\}$, and $f^{-1}(f(A))=\{1,2,3,4\}$. So, $f^{-1}(f(A)) \not\subset A$. \qed
\end{example*}
\item Suppose $B \subset Y$. How are the sets $B$ and $f(f^{-1}(B))$ related? Give a proof and/or example(s) to justify your answer. 

\textbf{Claim:} $f(f^{-1}(B)) \subset B$.

\begin{proof}
In the trivial case where $f^{-1}(B) = \emptyset$, $f(f^{-1}(B))$ must also be $\emptyset$, so clearly $f(f^{-1}(B)) \subset B$ and we are done. 

Now, suppose that $f^{-1}(B) \neq \emptyset$, and let $y \in f(f^{-1}(B))$. Since $y$ is in the image of $f^{-1}(B)$, there must be an $x \in f^{-1}(B)$ such that $f(x)=y$. Since $x$ is in the preimage of $B$, $f(x)$ must be in $B$. Therefore, $f(x)=y \in B$. Thus, $f(f^{-1}(B)) \subset B$.
\end{proof}

\textbf{Claim:} $B \not\subset f(f^{-1}(B))$.
\begin{example*} Consider the following function, $f:\{1,2,3\} \to \{4,5,6,7\}$, whose definition is given by the following figure:
\begin{center}
\begin{tikzpicture}
%put some nodes on the left
\foreach \x in {1,2,3}{
\node[inner sep=2pt] (d\x) at (0,4-\x) {\x};
}
\node[fit=(d1) (d2) (d3),ellipse,draw,minimum width=1cm] {}; 
%put some nodes on the center
\foreach \x[count=\xi] in {4,5,...,7}{
\node[inner sep=2pt] (r\xi) at (2,8-\x) {\x};
}
\node[fit=(r1) (r2) (r3) (r4),ellipse,draw,minimum width=1.5cm] {}; 
%put some nodes on the right
\draw[-latex] (d1) -- (r2);
\draw[-latex] (d2) -- (r3);
\draw[-latex] (d3) -- (r4);
\end{tikzpicture}
\end{center}
Let $B=\{4,5,6,7\}$. According to the figure above, $f^{-1}(B)=\{1,2,3\}$, and $f(f^{-1}(B))=\{5,6,7\}$. So, $B \not\subset f(f^{-1}(B))$.  \qed
\end{example*}
\end{enumerate}

\pagebreak
\item Give an example to show that an arbitrary (i.e. not necessarily finite) intersection of open sets in $\R^n$ need not be open. 
\begin{example*}
Consider the following set of open intervals:
$$S = \{ \left(0,\tfrac{n+1}{n}\right) : n \in \N \}.$$ 
Let $I_n$ denote the $n$th element of this set, that is, $I_n=(0,\tfrac{n+1}{n})$. Since the infimum of the set of upper bounds for these intervals is 1, 
$$\bigcap_{n=1}^{\infty}I_n=(0,1].$$
The set $(0,1]$ is not open because every open ball centered at 1 contains real numbers greater than 1, so cannot be a subset of $(0,1]$.
\qed
\end{example*}

\item Professor Doofus mistakenly writes the following on the blackboard.
\begin{romantheorem*}The following are equivalent.
\begin{enumerate}[label=(\arabic*)]
\item $f:\R^n \to \R^m$ is continuous at all $x \in \R^n$ (with the $\delta$-$\epsilon$ definition)
\item For every open set $U \subset \R^n$, the image $f(U) \subset \R^m$ is open. 
\end{enumerate}
\end{romantheorem*}
Give an example which shows why Doofus is wrong. 
\begin{example*}
Let $y \in \R^m$. Consider a constant function, $$f(x)=y, \quad \forall x \in \R^n.$$ 
The function $f$ is continuous because given any $\epsilon > 0$, we can let $\delta=1$, and if $x \in B(x_0, \delta)$, then $f(x) \in B(f(x_0), \epsilon)$ because $f(x)=f(x_0)=y$. So, (1) is true in this case. 

However, for any set $A \subset \R^n$, the image $f(A)=\{y\}$ is \emph{not} open. This is because for every $r>0$, the ball $B(y,r)$ contains points distinct from $y$, so it cannot be a subset of $\{y\}$. Therefore, (2) is false, so (1) and (2) are not equivalent statements. \qed
\end{example*}
\end{enumerate}

\end{document}