\documentclass[letterpaper]{article}
%\documentclass[a5paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[letterpaper,top=1in,bottom=1in,left=1in,right=1in,marginparwidth=1.75cm]{geometry}
%\usepackage[a5paper,top=1cm,bottom=1cm,left=1cm,right=1.5cm,marginparwidth=1.75cm]{geometry}

\input{tskpreamble}

\pgfplotsset{compat=1.13}

\title{Math 462 - Advanced Linear Algebra \linebreak
	Homework 1}
\author{Trevor Klar}

\begin{document}

\maketitle

\begin{proposition*}\emph{\textbf{(1-2)}} Let there be given functions $f:S \to T$ and $g:T \to U$. Then 
\begin{enumerate}[label=(\roman*)]
\setcounter{enumi}{4}
\item if $g \circ f$ is surjective, then so is $g$. 
\begin{proof}
Since $g \circ f$ is surjective, then for any $y \in U$, there exists an $x \in S$ such that $g \circ f(x) = y$. Now $x$ is in the domain of $f$, so $f(x)$ is in the domain of $g$, and by definition, $g(f(x))=g \circ f(x)=y$. Thus, for any $y \in U$, there exists $f(x) \in T$ such that $g(f(x))=y$, so $g$ is surjective.
\end{proof}
\end{enumerate}	
\end{proposition*}

\noindent \textbf{Exercises:}
\begin{enumerate}
\item Find sets $S$, $T$, and $U$ and functions $f:S \to T$ and $g: T \to U$ such that $g \circ f$ is injective, but $g$ is \emph{not} injective. (\emph{Hint}: The choice of $S=\{0\}$, $T=\{0,1\}$, and $U=\{0\}$ will inevitably lead to the desired result.)
\begin{example*}
Consider the following functions $f:S \to T$ and $g: T \to U$, whose definition is given by the following figure:
\begin{center}
\begin{tikzpicture}
%put some nodes on the left
\foreach \x in {1}{
\node[inner sep=2pt] (s\x) at (0,1-\x) {0};
}
\node[fit=(s1),ellipse,draw,minimum width=1cm] {}; 
%put some nodes on the center
\foreach \x[count=\xi] in {0,1}{
\node[inner sep=2pt] (t\xi) at (2,\x) {\x};
}
\node[fit=(t1) (t2),ellipse,draw,minimum width=1.5cm] {}; 
%put some nodes on the right
\foreach \x[count=\xi] in {1}{
\node[inner sep=2pt] (u\xi) at (4,1-\x) {0};
}
\node[fit=(u1),ellipse,draw,minimum width=1cm] {}; 
%draw the arrows
\draw[-latex] (s1) -- (t1);
\draw[-latex] (t1) -- (u1);
\draw[-latex] (t2) -- (u1);
%label the sets
\node[inner sep=2pt] (setS) at (0,-1) {$S$};
\node[inner sep=2pt] (setT) at (2,-1) {$T$};
\node[inner sep=2pt] (setU) at (4,-1) {$U$};
\node[inner sep=2pt] (funcF) at (.85,0.25) {$f$};
\node[inner sep=2pt] (funcG) at (3,0.2) {$g$};
\end{tikzpicture}
\end{center}
\end{example*}
In this example, $g \circ f$ is injective (vacuously) because for any two $x,y \in S$; $x \neq y \implies g \circ f(x) \neq g \circ f(y)$. This is also more intuitively clear if one recalls that injectivity is also called one-to-one, and since $g \circ f$ contains only the mapping $0 \mapsto 0$, then clearly $g \circ f$ is one-to-one. 

Secondly, $g$ is not injective because $0 \neq 1$, however $g(0)=g(1)=0$. \qed

\item Find sets $S$, $T$, and $U$ and functions $f:S \to T$ and $g: T \to U$ such that $g \circ f$ is surjective, but $f$ is \emph{not} surjective.
\begin{example*}
Actually, the same example for problem (1) will also work for this problem. The composition $g \circ f$ is surjective, because for every $y \in U$ (there is only one), there exists an $x \in S$ such that $g \circ f(x)=y$ ($x=0$). However, $f$ is not surjective because for $y=1$, there does not exist any $x \in S$ such that $f(x)=y$. \qed
\end{example*}

\item Find a non-identity function $f:\R \to \R$ which is its own inverse function. That is, $f \circ f = 1_\R$ or, equivalently, $f(f(x))=x$ for all real $x$. 
\begin{example*}
Let $f(x)=-x$. Then, for all real $x$, $f(x)=-x$, and $f(f(x))=x$. \qed
\end{example*}

\setcounter{enumi}{4}
\item Find a bijective map from the open interval $(\sfrac{-\pi}{2}, \sfrac{+\pi}{2})$ to the set $\R$ of real numbers. This shows, by the way, that both sets have the same cardinality.
\begin{example*}
Let $f:(\sfrac{-\pi}{2}, \sfrac{+\pi}{2}) \to \R$ be defined as $f(x) = \tan(x) = \frac{\sin(x)}{\cos(x)}$. 

We will now show that $f$ is 1-1 and onto. For any two numbers $x_1, x_2 \in (\sfrac{-\pi}{2}, \sfrac{+\pi}{2})$,
$$x_1 \neq x_2 \implies \tan(x_1) \neq \tan(x_2),$$
since $\tan(x)$ is a strictly increasing function. So, $f$ is 1-1. 

Since $\tan(x)$ for an angle $x$ is also defined as the ratio of the opposite leg to the adjacent leg in a right triangle having one angle $x$, we can show that $f$ is surjective. Let $y$ be any arbitrary real number. Now, construct a right trangle with perpendicular sides of length $y$ and $1$. It follows that this triangle has an angle whose tangent is $y$. Thus, $\forall y \in \R, \exists x \in (\sfrac{-\pi}{2}, \sfrac{+\pi}{2})$ such that $\tan(x)=y$, so $f$ is surjective. \qed 
\end{example*}

\item Explicitly construct a bijective function from the set of integers $\Z$ to the set of even integers $2\Z$. 
\begin{example*}
Let $f:\Z \to 2\Z$ be defined as 
$$f(x) = 2x.$$
By definition of an even integer, for every $y \in 2\Z$, there exists an integer $x$ such that $2x=y$. Therefore, $f$ is surjective.

Secondly, if $x \neq y$, then either $x < y$ or $x > y$. Without loss of generality, call $y$ the greater number, so that $x < y$. By the multiplication property of inequality, $2x < 2y$. Therefore, $2x \neq 2y$. We have shown that $x\neq y \implies 2x \neq 2y$, so $f$ is injective. \qed
\end{example*}
\end{enumerate}

\end{document}