\frame{
  \frametitle{More Examples}

  \begin{enumerate}
    \setcounter{enumi}{2}
  \item What is the minimum of $f(x)=(x+2)(x+4)+3$?

    \begin{center}
      A $=0$
      \quad 
      B $ = 1$
      \quad 
      C $= 2$
      \quad 
      D $= 3$
      \quad 
      E $= 4$
      \pause
      \quad
    \end{center}
    \alert{Answer:}\ \answer{C}
    \pause
    \bigskip

    \item What is minimum of $f(x)=x^2 + 16 x^{-2}$?
      \begin{center}
        A $=2$
        \quad 
        B $= 4$
        \quad 
        C $= 6$
        \quad 
        D $= 8$
        \quad 
        E $= 16$
        \pause
      \end{center}
      \alert{Answer:}\ \answer{D}
      \pause
      \medskip

      \item Find the value of $x$ which makes $f(x)=-e^x-e^{-2x}$ a
        maximum. 
        \begin{center}
          A $=0$
          \quad 
          B $= \ln(2)$
          \quad 
          C $=-\ln(2)$
          \quad 
          D $= \ln(2)/3$
          \quad 
          E $= \ln(2)/3$
          \pause
        \end{center}
        \medskip
        \alert{Answer:}\ \answer{E}

      \end{enumerate}

}


\frame{ 
  \frametitle{Word Problem \#3} 

  A fenced garden with an area of $100\ \text{m}^2$  will be made in
  the shape of a rectangle. It will be surrounded on all four sides by
  a fence. What length and width should be used so the least amount of
  fence is needed? 
  \bigskip
  \pause

  \alert{Approach:}
  \begin{itemize}
  \item[{\blue(1)}] Express the total length of fence in terms of
    \emph{only}\ one variable, either $L = $ length of field, or $W =$
    width of field. This gives a formula for $P=$ (total length of
    fence) involving, say, $W$.
    \pause
    \smallskip

  \item[{\blue(2)}] Find minimum by solving $\dfrac{dP}{dW}=0$.
  \end{itemize}
  \pause
  \bigskip

  Students always find {\blue(1)}\ the hardest part.

  \alert{You}\ have been prepared for this by word problems from chapter 3!
 
  

}



\frame{
  \frametitle{Word Problem \#4 (a sequel!)}

  A fenced garden with an area of $1000\ \text{m}^2$  will be made in
  the shape of a rectangle. It will be surrounded on all four sides by
  a fence. Three sides are wood fence, and the remaining side is a
  brick wall.
  \begin{itemize}
  \item The wood fence costs \$5 per meter length.
  \item The brick wall costs \$20 per meter length.
    \pause
  \item $C=$ total cost of the fence and brick wall
  \item $L=$ length of the brick wall
  \item $W=$ width of the other side 
  \end{itemize}
  \begin{enumerate}
  \item[\colorbox{blue!50}{(a)}] Find a formula for $C$ in terms of only $L$.
    \vspace*{-0.5em}

    \begin{center}
      A $= 2W + 2L$
      \quad 
      B $= 2000L^{-1}+2L$
      \quad 
      C $= 25L +10000L^{-1}$\\[0.5em] 
      % 
      \ \quad
      D $= 20L + 10000WL^{-1}$
      \quad 
      E $= 5L + 3000$
      \pause
      \quad
      \answer{C}
    \end{center}
    % \bigskip

  \item[\colorbox{blue!50}{(b)}]
    What length of brick wall gives lowest cost?
    \vspace*{-0.5em}

    \begin{center}
      A $= 20$
      \quad 
      B $= 40$
      \quad 
      C $= 50$
      \quad 
      D $= 100$
      \quad 
      E $= 25$
      \pause
      \quad
      \answer{A}
    \end{center}
  \end{enumerate}

}





