\documentclass[letterpaper]{article}
%\documentclass[a5paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}


%% Sets page size and margins
\usepackage[letterpaper,top=.75in,bottom=1in,left=1in,right=1in,marginparwidth=1.75cm]{geometry}
%\usepackage[a5paper,top=1cm,bottom=1cm,left=1cm,right=1.5cm,marginparwidth=1.75cm]{geometry}

\usepackage{graphicx}
%\graphicspath{../images}	  %%where to look for images

\input{../tskpreamble}

\pgfplotsset{compat=1.13}

%\newcommand{\T}{\mathcal{T}}
%\newcommand{\B}{\mathcal{B}}

%These commands are now in tskpreamble_nothms.tex, but are left as a comment here for reference. 
%\newcommand{\arbcup}[1]{\bigcup\limits_{\alpha\in\Gamma}#1_\alpha}
%\newcommand{\arbcap}[1]{\bigcap\limits_{\alpha\in\Gamma}#1_\alpha}
%\newcommand{\arbcoll}[1]{\{#1_\alpha\}_{\alpha\in\Gamma}}
%\newcommand{\arbprod}[1]{\prod\limits_{\alpha\in\Gamma}#1_\alpha}
%\newcommand{\finitecoll}[1]{#1_1, \ldots, #1_n}
%\newcommand{\finitefuncts}[2]{#1(#2_1), \ldots, #1(#2_n)}
%\newcommand{\abs}[1]{\left|#1\right|}
%\newcommand{\norm}[1]{\left|\left|#1\right|\right|}

\title{Math 360 \linebreak
Section 1.1 Exercises}
\author{Trevor Klar}

\begin{document}

\maketitle

\begin{enumerate}
\item 
	\begin{enumerate}
	\item $b*d=e$
	\item $c*c=b$
	\item $[(a*c)*e]*a = [c*e]*a = a*a = a$
	\end{enumerate}
\item[7.] $*$ is clearly not commutative, since $1*2\neq 2*1$. Observe the following to see that $*$ is not associative either: $(1*2)*3=-1*3=-4$, whereas $1*(2*3)=1*-1=2$.
\item[9.] $*$ is commutative, since $\frac{ab}{2}=\frac{ba}{2}$. Also, $*$ is associative, since $(a*b)*c = \frac{ab}{2}*c = \frac{abc}{4} = a*\frac{bc}{2} = a*(b*c)$.
\item[11.] $*$ is commutative, since ${2}^{ab}={2}^{ba}$. However, $*$ is not associative, since $(3*5)*7=2^{15}*7=2^{(7)(2^{15})}$, but $3*(5*7)=3*2^{35}=2^{(3)(2^{35})}$. 
\item[13.] For a set of 2 elements, consider the table: 
\[\begin{array}{c!c|c}
* & a & b \\
\thickhline
a & x_1 & x_2\\
\hline
b & x_2 & x_3\\
\end{array}\]
There are three unique outputs, $x_1, x_2, x_3$, and each one can map to one of two possible values, so there are $2^3=8$ possible commutative binary operations on a set of 2 elements. 

For 3 elements, the table gives 
\[\begin{array}{c!c|c|c}
* & a & b & c\\ \thickhline
a & x_1 & x_2 & x_4 \\ \hline
b & x_2 & x_3 & x_5 \\ \hline
c & x_4 & x_5 & x_6
\end{array}\]
Thus, there are 6 unique outputs, which can each take 3 possible values. Therefore there are $3^6$ possible commutative binary operations on a set of 3 elements. 

As we increase the number of elements from $n-1$ to $n$, we see that the number of unique outputs increases by $n$. Thus, the number of unique outputs for a set of $n$ elements is given by the $n$-th triangle number. Thus, the number of possible commutative binary operations on a set of $n$ elements is given by 
$$ n^{T_n}, $$
where $T_n=\frac{(n)(n+1)}{2}$ is the $n$-th triangle number.
\item[14.] A binary operation $*$ on a set $S$ is \emph{commutative} if and only if, for all $a,b\in S$, we have $a*b=b*a$. 
\item[15.] A binary operation $*$ on a set $S$ is \emph{associative} if and only if, for all $a,b,c\in S$, we have $(a*b)*c=a*(b*c)$. 
\item[16.] A subset $H$ of a set $S$ is \emph{closed} under $*$ if and only if, for all $a,b\in H$, we have $(a*b)\in H$. 

\textbf{For Exercises 17-22, determine if $*$ is a binary operation on $S$. If not, state whether Condition 1, Condition 2, or both are violated. }
\item[17.] On $\Z^+$, define $*$ by $a*b=a-b$. 
\textbf{Answer: } No. Condition 2 is violated since $1,2\in \Z^+$, but $1*2=-1\not\in\Z^+$. 
\item[19.] On $\R$, define $*$ by $a*b=a-b$. This is of course a binary operation. For every subtraction problem, there is exactly one answer, and every difference of real numbers is a real number. 
\item[21.] On $\Z^+$, define $a*b=c$, where $c$ is at least 5 more than $a+b$. \textbf{Answer: } No. Condition 1 is violated, since there are infinitely many real numbers $c$ such that $c\geq a+b+5$. 
\item[23.] Let $H$ be the subset of $M_2(\R)$ consisting of all matrices of the form 
$\arraycolsep=1.4pt\def\arraystretch{1}
\left[\begin{array}{lr}
a & -b \\
b & a \\
\end{array} \right]$ 
for $a,b\in \R$. Is $H$ closed under
\begin{enumerate}
	\item[a.] matrix addition?
	\item[b.] matrix multiplication?
\end{enumerate}

\textbf{Answer to a:} Yes. Adding two arbitrary elements of $H$, we find  
$\arraycolsep=1.4pt\def\arraystretch{1}
\left[\begin{array}{lr}
a & -b \\
b & a \\
\end{array} \right]
+
\arraycolsep=1.4pt\def\arraystretch{1}
\left[\begin{array}{lr}
c & -d \\
d & c \\
\end{array} \right] 
=
\arraycolsep=1.4pt\def\arraystretch{1}
\left[\begin{array}{lr}
a+c & \, \, -(b+d) \\
b+d & a+c\phantom{)} \\
\end{array} \right],$
which is an element of $H$.  

\textbf{Answer to b:} Yes. Multiplying two arbitrary elements of $H$, we find  
$\arraycolsep=1.4pt\def\arraystretch{1}
\left[\begin{array}{lr}
a & -b \\
b & a \\
\end{array} \right]
\arraycolsep=1.4pt\def\arraystretch{1}
\left[\begin{array}{lr}
c & -d \\
d & c \\
\end{array} \right] 
=
\arraycolsep=1.4pt\def\arraystretch{1}
\left[\begin{array}{lr}
ac-bd & \, \, \, -(ad+bc) \\
ad+bc & ac-bd\phantom{)} \\
\end{array} \right],$
which is an element of $H$.  

\item[24.] 
	\begin{enumerate}[label=\alph*.]
	\item F
	\item T
	\item F
	\item F
	\item F
	\item T
	\item F
	\item F
	\item T
	\item F
	\end{enumerate}

\item[26.] Prove that if $*$ is and associative and commutative binary operation on a set $S$, then 
$$(a*b)*(c*d)=[(d*c)*a]*b$$
for all $a,b,c,d\in S$. 
\begin{proof}
\[\begin{array}{rcll}
(a*b)*(c*d) &=& (c*d)*(a*b) & \text{commutative property}\\
&=& (d*c)*(a*b) & \text{commutative property}\\
&=& [(d*c)*a]*b & \text{associative property}\\
\end{array}\]
\end{proof}

\textbf{In 27 and 28, prove or give a counterexample.}
\item[27.] Every binary operation on a set consisting of a single element is both commutative and associative.
\begin{proof}
Denote our singleton set as $S=\{e\}$, and let $*$ be a binary operation on $S$. Applying the definition of commutativity, we can see that $*$ is commutative: for all $a,b\in S$, we have that $a*b=b*a$. To see this, observe that since $a\in S, a=e$. Also, since $b\in S, b=e$. Thus, $a*b=e*e=b*a$. 

We can apply the definition of associativity similarly if we observe that $e*e$ can only have one possible result: $e*e=e$. Thus, for all $a,b,c\in S$, 
\[\begin{array}{rcl}
(a*b)*c&=&(e*e)*e\\
&=&e*e\\
&=&e*(e*e)\\
&=&a*(b*c)\\
\end{array}\]
and we are done. \end{proof}

\item[28.] Every commutative binary operation on a set having just two elements is associative. 

\textbf{Counterexample:} Consider the set $S=\{\blacksquare, \square\}$, with $*$ defined by the following table:
\[\begin{array}{c!c|c}
* & \blacksquare & \square \\
\thickhline
\blacksquare & \square & \blacksquare\\
\hline
\square & \blacksquare & \blacksquare\\
\end{array}\]
We will show that $(\square*\blacksquare)*\blacksquare \neq \square*(\blacksquare*\blacksquare)$, and thus the associative property does not hold. 
$$(\square*\blacksquare)*\blacksquare = \blacksquare*\blacksquare = \square,$$
however, 
$$\square*(\blacksquare*\blacksquare)=\square*\square=\blacksquare.$$
Thus $*$ on $S$ is not commutative (observe that the table is symmetric), but not associative. \qed

\item[41.] This is the state diagram for a machine which determines if the input string has at least two $c$'s. If the final state is $s_2$, then the input string has at least two $c$'s.

\jpg{scale=.5}{360_hw1-1_prob_41}

\item[42.] This is the state diagram for a machine which determines if the input string has exactly 3 $c$'s. If the final state is $s_3$, then the input string has exactly 3 $c$'s. Note that if the final state is $s_f$, then the input string has greater than 3 $c$'s, and if the final state is $s_0, s_1,$ or $s_2$, then the input string has less than 3 $c$'s. 

\jpg{scale=.5}{360_hw1-1_prob_42}

\item[43.] This is the state diagram for a machine which determines if the number of 1's in the input string is congruent to 0, 1, or 2 modulo 3. $s_0$ is the initial state, and corresponds to $0\equiv 0$ mod 3. The subscript of the final state gives the result. 

\jpg{scale=.5}{360_hw1-1_prob_43}



\end{enumerate}
\end{document}
